---
title: "Analysis of School Shootings in the US 1990 - "
author: "Zhiling Chen, Yihan Zhou, Jiatong Lyu"
output:
  html_document:
    fig_width: 8
    code_folding: hide
    highlight: tango
    toc: true
    toc_float:
      collapsed: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=4,
                      echo=FALSE, warning=FALSE, message=FALSE)
```

# Data Set Overview

The following data set is looking at school shootings in the US from 1990 to present.This data set was retrieved from kaggle. The data includes the data, city, state, area type, school, fatalities, wounded, dupe, source and desc. Furthermore, the data set includes information regarding Census numbers on elementary school, high school and college populations through 2016.

# Goal of Analysis

The goal of the analysis is to get a better understanding of the victims / suspects that are involved in school shootings. Some questions to ask, 

# Data Prep

# Quiz Grade Analysis

The following report looks at the performance of 30 students over 4 quizzes. The grades data is simulated using random numbers for normal distributions.

## Grades Dataset 

The following data frame captures the grades of 30 students.

```{r echo=TRUE}
library(plotly)

set.seed(123)

data <- data.frame(
  Quiz1 = round(rnorm(30, 60, 5)),
  Quiz2 = round(rnorm(30, 70, 2)),
  Quiz3 = round(rnorm(30, 80, 5)),
  Quiz4 = round(rnorm(30, 75, 10))
  )

data$Average_Quizzes <- round(
  (data$Quiz1 + data$Quiz2 + data$Quiz3 + data$Quiz4) / 4.0)

data <- data[order(data$Average_Quizzes, decreasing = T), ]

grades <- data$Average_Quizzes

x <- list(
  title = "Student"
)
y <- list(
  title = "Score"
)


n = length(grades)

p <- plot_ly(x = 1:n, y = grades, name = 'Quizzes', type = 'bar') %>%
  layout(title="Average Quiz Scores", xaxis = x, yaxis = y)
p
```


## Summary of Quiz scores

```{r echo = TRUE}

options(digits=2)
sum_data <- data.frame(
  AvgQuiz = as.vector(summary(data$Average_Quizzes)),
  Quiz1 = as.vector(summary(data$Quiz1)),
  Quiz2 = as.vector(summary(data$Quiz2)),
  Quiz3 = as.vector(summary(data$Quiz3)),
  Quiz4 = as.vector(summary(data$Quiz4))
)

rownames(sum_data) <- c("Min", "Q1", "Q2", "Mean", "Q3", "Max")
sum_data

```


# Box plot analysis

```{r echo = TRUE}

plot_ly(data, y = ~Average_Quizzes, type="box", name = 'Avg_Quiz') %>%
  add_trace(p, y = ~Quiz1, name = 'Quiz1') %>%
  add_trace(p, y = ~Quiz2, name = 'Quiz2') %>%
  add_trace(p, y = ~Quiz3, name = 'Quiz3') %>%
  add_trace(p, y = ~Quiz4, name = 'Quiz4') %>%
  layout(yaxis = y)

```

# Conclusions
conclusionsssss
Add conclusions about the analysis...
